Testable normative theories

### 2020-05-03 simple.tex
Started analysis of conditions for no contradictory conclusions

\subsection{Classify propositions}
A normative theory starts with an axiom stating its normative adequacy.
\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$]
	A general normative theory is \emph{normatively adequate} iff $\forall \phi \in \Phi$: 
	\begin{equation}
		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ 
		\begin{cases}
			\phi \in \iphi,\\
			\lnot\phi \notin \iphi.
		\end{cases}
	\end{equation}
\end{axiom}

This notation is justified only if it is impossible that both $\phi \in \iphi$ and $\phi \notin \iphi$ be implied. \commentOC{TODO clarify.} The following conditions permit to obtain this result.

>>>>

\subsection{Classify propositions}
The notations $\iphi$ and $\iphibar$ designate subsets of $\Phi$, representing the propositions that $i$ accepts and rejects, respectively.

\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$ 1]
	$\forall \phi \in \Phi$: 
	\begin{equation}
		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iphi.
	\end{equation}
\end{axiom}
\begin{axiom}[Normative adequacy of $\allargs$ and $\ileadstost$ 2]
	$\forall \phi \in \Phi$: 
	\begin{equation}
		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \lnot\phi \in \iphibar.
	\end{equation}
\end{axiom}
\begin{axiom}[Coherent complement]
	$\forall \phi \in \Phi: \phi \in \iphi ⇒ \phi \notin \iphibar$.
\end{axiom}

\begin{definition}[Coherent protocol]
	$\forall \phi \in \Phi: \ar \ileadstost \phi ⇒ \ar \nileadstost ¬\phi$.
\end{definition}

\begin{theorem}
	Under axioms of Normative adequacy, Coherent complement ⇒ Coherent protocol.
\end{theorem}
\begin{proof}
	Coherent complement is equivalent to $\forall \phi \in \phi: ¬(\phi \in \iphi \land \phi \in \iphibar)$.
	Coherent protocol is equivalent to $\forall \phi \in \Phi: ¬(\ar \ileadstost \phi \land \ar \ileadstost ¬\phi)$, which implies (using Norm ad 1 and 2) $\forall \phi \in \Phi: ¬(\phi \in \iphi \land \phi \in \iphibar)$.
\end{proof}

\begin{theorem}
	Under axioms of Normative adequacy, Coherent protocol ⇒ Coherent complement.
\end{theorem}
\begin{proof}
	This is false under the current definitions: if $\ileadstost = \emptyset$, coherent protocol, but $\phi \in \iphi \land \phi \in \iphibar$ possible.
\end{proof}

\begin{axiom}[Coherent negation]
	$\forall \phi \in \Phi: \phi \in \iphi ⇔ ¬\phi \in \iphibar$.
\end{axiom}
This notation (writing $\phi \in \iphibar$ as equivalent to $\phi \notin \iphi$) is justified only if it is impossible that both $\phi \in \iphi$ and $\phi \notin \iphi$ be implied (thus, if Coherent complement). \commentOC{TODO clarify.} The following conditions permit to obtain this result. \commentOC{Cond. 1 is stronger than necessary: we could have ¬cond. 1 and still Coh compl: $(\ar_2, \ar_1) \ileadstost \phi$ and $(\ar_2, \ar_1) \ileadstost ¬\phi$ without problems if $\ar_2$ and $\ar_1$ are not decisive. In fact, $(\ar_2, \ar_1) \ileadstoe ¬\phi$ should be defined as $(\ar_2, \ar_1) \nileadstost \phi) \lor (\ar_2, \ar_1) \ileadstost ¬\phi$, just in case a strange protocol allows both leading always to $\phi$ and $¬\phi$, and I think the rest goes through.}
